Missing The Point

### 2020-10-12 Manuscript.Rmd
Add automatically updated references

---
title: "Missing The Point"
author: "Hanne Oberman"
date: "7-9-2020"
output: html_document
---

@@

Missing data pose a ubiquitous threat to anyone who aims to obtain unbiased, confidence-valid statistical inferences. A popular technique to accommodate missing data is to 'impute' (i.e., fill in) any missing values in an incomplete dataset. Imputation procedures like 'Multiple Imputation by Chained Equations' (MICE) have proven to be powerful tools to draw valid inferences under many missing data circumstances (Rubin, 1987; van Buuren, 2018). Most imputation software packages rely on iterative algorithms to obtain imputed values.

@@

In this paper we explore diagnostic methods for iterative imputation algorithms. For reasons of brevity, we focus on the iterative imputation algorithm implemented in the popular `mice` package (REF) in `R` (REF). We consider two tested non-convergence identifiers for MCMC algorithms: autocorrelation (conform Lynch, 2007, p. 147) and potential scale reduction factor $\widehat{R}$ (conform Vehtari et al., 2019, p. 5).  MICE, and show which method (parameter + diagnostic + threshold) is the most informative about convergence

@@

as soon as we start downweighting the first few it from the calc, the memory effect would

@@

plotfun(v="est")
plotfun(v="ac.max.qhat") #+ list(scale_y_continuous(limits = c(0.65,1)))
plotfun(v="ac.max.lambda")
plotfun(v="r.hat.max.qhat")+list(geom_hline(yintercept = 1.2, color = "grey"), scale_y_continuous(limits = c(1,2)))
plotfun(v="r.hat.max.lambda")+list(geom_hline(yintercept = 1.2, color = "grey"), scale_y_continuous(limits = c(1,2)))

@@

>>>>

---
title: "Missing The Point"
author: "Hanne Oberman"
date: "7-9-2020"
output: html_document
bibliography: ref.bib
---

@@

Missing data pose a ubiquitous threat to anyone who aims to obtain unbiased, confidence-valid statistical inferences. A popular technique to accommodate missing data is to 'impute' (i.e., fill in) any missing values in an incomplete dataset. Imputation procedures like 'Multiple Imputation by Chained Equations' (MICE) have proven to be powerful tools to draw valid inference under many missing data circumstances (Rubin, 1987; van Buuren, 2018). To obtain imputations, most imputation software packages rely on iterative algorithms.

@@

In this paper we explore diagnostic methods for iterative imputation algorithms. For reasons of brevity, we focus on the iterative imputation algorithm implemented in the popular `mice` package [@mice] in `R` [@R]. We consider two non-convergence identifiers for iterative algorithms: autocorrelation (conform Lynch, 2007, p. 147) and potential scale reduction factor $\widehat{R}$ (conform Vehtari et al., 2019, p. 5). Aside from the usual parameters to monitor---chain means and chain variances---we also investigate convergence in the multivariate state-space of the algorithm.

We propose a novel multivariate parameter to check for non-convergence in iterative algorithms. Our aim is to show which method (parameter + diagnostic + threshold) is the most informative about non-convergence in the iterative imputation algorithm implemented in `mice`.

@@

as soon as we start down-weighting the first few it from the calc, the memory effect would

@@

plotfun(v="est")
plotfun(v="ac.max.qhat") #+ list(scale_y_continuous(limits = c(0.65,1)))
plotfun(v="ac.max.lambda")
plotfun(v="r.hat.max.sigma.hgt")+list(geom_hline(yintercept = 1.2, color = "grey"), scale_y_continuous(limits = c(1,2)))
plotfun(v="r.hat.max.qhat")+list(geom_hline(yintercept = 1.2, color = "grey"), scale_y_continuous(limits = c(1,2)))
plotfun(v="r.hat.max.lambda")+list(geom_hline(yintercept = 1.2, color = "grey"), scale_y_continuous(limits = c(1,2)))

@@

# References
